---
title: "NPP delivery - National & Regional"
output:
  beamer_presentation:
    latex_engine: pdflatex
    slide_level: 2
    toc: false
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
##always_allow_html: true
---

```{r libraries, include=FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(ggrepel)
library(ggpubr)
library(gridExtra)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')

source(knitr::purl("NPP_activity_functions.Rmd", output = tempfile()))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## NPP activity to date against previous year's delivery

```{r plot chart, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "National")
```

## NPP activity to date against previous year's delivery - East Of England

```{r plot chart reg1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "East Of England")
```

## NPP activity to date against previous year's delivery - London

```{r plot chart reg2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "London")
```

## NPP activity to date against previous year's delivery - Midlands

```{r plot chart reg3, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "Midlands")
```

## NPP activity to date against previous year's delivery - North East And Yorkshire

```{r plot chart reg4, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "North East And Yorkshire")
```

## NPP activity to date against previous year's delivery - North West

```{r plot chart reg5, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "North West")
```

## NPP activity to date against previous year's delivery - South East

```{r plot chart reg6, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "South East")
```

## NPP activity to date against previous year's delivery - South West

```{r plot chart reg7, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot_npp_activity_monitoring(level = "Regional", 
                             region_STP_name = "South West")
```
