---
title: "Dental Data Pack"
subtitle:  "National"
author: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  beamer_presentation:
    latex_engine: pdflatex
    slide_level: 2
    toc: true
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
##always_allow_html: true
---

```{r libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(ggrepel)
library(ggpubr)
library(gridExtra)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')


```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r variables for summary, include = FALSE}
latest_month <- max(UOA_calendar_data$month)

latest_month_formatted <- format(latest_month, "%B %Y")

latest_final_month <- max(UDA_calendar_data$month[UDA_calendar_data$final_yn == "Y"])

latest_final_month_formatted <- format(latest_final_month, "%B %Y")

previous_month <- latest_final_month %m-% months(1)

previous_month_formatted <- format(previous_month, "%B %Y")

provisional_month1_formatted <- format(latest_final_month %m+% months(1), "%B")

provisional_month2_formatted <- format(latest_final_month %m+% months(2), "%B")

n_contracts_uda <- prettyNum(n_distinct(UDA_calendar_data$contract_number[UDA_calendar_data$month == latest_final_month]),
                             big.mark = ",")

uda_delivered <- prettyNum(data_Nat_UDA$UDAs_delivered_month[data_Nat_UDA$calendar_month == format(latest_final_month, "%Y-%m")],
                           big.mark = ",")

uda_diff <- prettyNum(data_Nat_UDA$UDAs_delivered_month[data_Nat_UDA$calendar_month == format(latest_final_month, "%Y-%m")] 
                      - data_Nat_UDA$UDAs_delivered_month[data_Nat_UDA$calendar_month == format(previous_month, "%Y-%m")],
                      big.mark = ",")

ytd_uda_delivery <- prettyNum(data_Nat_YTD_UDA$YTD_delivery[data_Nat_YTD_UDA$calendar_month == format(latest_final_month, "%Y-%m")],
                              big.mark = ",")

uda_delivery_pct <- data_Nat_UDA$UDAs_delivered_month_percent_contracted_standardised[data_Nat_UDA$calendar_month == format(latest_final_month, "%Y-%m")]

unique_adults <- prettyNum(data_Nat_unique$unique_adults_seen_24_month[data_Nat_unique$calendar_month == format(latest_final_month, "%Y-%m")],
                           big.mark = ",")

adults_diff <- prettyNum(data_Nat_unique$unique_adults_seen_24_month[data_Nat_unique$calendar_month == format(latest_final_month, "%Y-%m")] - 
  data_Nat_unique$unique_adults_seen_24_month[data_Nat_unique$calendar_month == format(previous_month, "%Y-%m")],
  big.mark = ",")

unique_children <- prettyNum(data_Nat_unique$unique_children_seen_12_month[data_Nat_unique$calendar_month == format(latest_final_month, "%Y-%m")],
                           big.mark = ",")

children_diff <- prettyNum(data_Nat_unique$unique_children_seen_12_month[data_Nat_unique$calendar_month == format(latest_final_month, "%Y-%m")] - 
  data_Nat_unique$unique_children_seen_12_month[data_Nat_unique$calendar_month == format(previous_month, "%Y-%m")],
  big.mark = ",")

npp_adults <- prettyNum(npp_nat$adult_NPP_patients_seen[npp_nat$calendar_month == format(latest_final_month, "%Y-%m")],
                        big.mark = ",")

npp_adult_diff <- prettyNum(npp_nat$adult_NPP_patients_seen[npp_nat$calendar_month == format(latest_final_month, "%Y-%m")] - 
  npp_nat$adult_NPP_patients_seen[npp_nat$calendar_month == format(previous_month, "%Y-%m")],
  big.mark = ",")

npp_children <- prettyNum(npp_nat$child_NPP_patients_seen[npp_nat$calendar_month == format(latest_final_month, "%Y-%m")],
                          big.mark = ",")

npp_child_diff <- prettyNum(npp_nat$child_NPP_patients_seen[npp_nat$calendar_month == format(latest_final_month, "%Y-%m")] - 
  npp_nat$child_NPP_patients_seen[npp_nat$calendar_month == format(previous_month, "%Y-%m")],
  big.mark = ",")

n_contracts_uoa <- prettyNum(n_distinct(UOA_calendar_data$contract_number[UOA_calendar_data$month == latest_month]),
                             big.mark = ",")

ytd_uoa_delivery <- prettyNum(data_Nat_YTD_UOA$YTD_delivery[data_Nat_YTD_UOA$calendar_month == format(latest_month, "%Y-%m")],
                              big.mark = ",")
```

# Introduction

## Introduction

This slide pack has been streamlined to help users to easily access the most important information. This change took effect as of June 2024 data. As part of this change we have also sought to make the slides more useful by making the following changes:

-   Swapping from scheduled data (the month the dentist claimed for payment following a finished course of treatment) to calendar month data (the month the course of treatment finished). This change better reflects the activity of dentists.
-   Including only GDS/PDS/PDS+ contracts where total contracted UDAs \>100. This means contracts with low UDA targets are excluded because they are usually not monitored against UDA delivery.
-   A national HTML will no longer be produced, instead the data is in an Excel file available alongside this pack.

&nbsp; <!--This is to force a line break-->

This pack will continue to evolve and change, any questions/comments should be directed to [england.primarycare.phodsdata\@nhs.net](mailto:england.primarycare.phodsdata@nhs.net)

## Calendar vs scheduled data

Analyses in this report now only use **calendar data**. Previous packs used scheduled data. An explanation on the difference is given below. The appendix also provides more detail on how the switch effects the data.

#### Calendar data explanation

-   Calendar data represents the month that a Course of Treatment (CoT) was completed.
-   For calendar data, if a CoT was completed in February but not declared till March, that activity would still be recorded as occurring in February.

#### Scheduled data explanation

-   Scheduled data represents the month that a Course of Treatment (CoT) was claimed for in the BSA Compass system.
-   For scheduled data, if a CoT was completed in February but not declared till March, the financial activity would recorded as occurring in March.

&nbsp; <!--This is to force a line break-->

The swap to using calendar data allows us to more accurately see what activity is happening per month rather than what payments are being claimed per month.

&nbsp;<!--This is to force a line break-->

Note that following a finished Course of Treatment (CoT), dentists have 62 days to declare their activity via FP17 forms to the BSA Compass system. This means when using calendar data, the most recent two months data are incomplete and subject to change. Therefore, the data that is provisional will be identified via a dashed line where possible and data labels on graphs will be for the most recent final month's data.

# Summary

## Summary

#### Dental

-   `r provisional_month1_formatted` and `r provisional_month2_formatted` data is subject to change for dental data. `r latest_final_month_formatted` data is referenced here in the summary.
-   Count of dental contracts included (`r latest_final_month_formatted`): `r n_contracts_uda`.
-   UDA delivery for most recent final month (`r latest_final_month_formatted`): `r uda_delivered`, a change of `r uda_diff` from previous month (`r previous_month_formatted`), standardised to allow for differing month lengths.
-   Year to date UDA delivery for most recent final month (`r latest_final_month_formatted`): `r ytd_uda_delivery` and as percentage of annual contracted UDAs: `r uda_delivery_pct`%.
-   Unique adults seen in the last 24 months as at `r latest_final_month_formatted`: `r unique_adults`, a change of `r adults_diff` from previous month (`r previous_month_formatted`).
-   Unique children seen in the last 12 months as at `r latest_final_month_formatted`: `r unique_children`, a change of `r children_diff` from previous month (`r previous_month_formatted`).
-   Adults seen as part of New Patient Premium scheme as at `r latest_final_month_formatted`: `r npp_adults`, a change of `r npp_adult_diff` from previous month (`r previous_month_formatted`).
-   Children seen as part of New Patient Premium scheme as at `r latest_final_month_formatted`: `r npp_children`, a change of `r npp_child_diff` from previous month (`r previous_month_formatted`).

#### Orthodontics

-   Count of orthodontic contracts included (`r latest_month_formatted`): `r n_contracts_uoa`.
-   Orthodontic activity is subject to change within a financial year. As of `r latest_month_formatted` year to date UOA delivery is `r ytd_uoa_delivery`.

# Units of Dental Activity (UDA) Information

## Units of Dental Activity - Calendar activity data standardised by working days

```{r UDA_activity_Calendar2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                              level = "National",
                              region_STP_name = NULL)
```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

## Units of Dental Activity - Calendar year to date delivery

```{r YTD UDA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "National",
                          region_STP_name = NULL,
                          plotChart = TRUE,
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

## Units of Dental Activity - Monthly activity compared to previous financial year

```{r monthly UDAs, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height = 5, fig.align = 'center'}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data,
                                   level = "National", 
                                   region_STP_name = NULL)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

-   This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
-   Some of the difference between months may be due to differences in the number of working days. The table shows the number of working days in each month for 2023/24 and 2024/25.
-   As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

## Banded courses of treatment standardised by working days (including Foundation Dentists (FD))

```{r banded CoT 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align="center"}
plot_banded_CoT(data = UDA_calendar_data_FD, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

## Banded Courses of Treatment as % of February 2020 delivery (including FD)

```{r banded CoT 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data_FD, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

# Dental Care Practitioners (DCPs) Information

## Percentage of total Courses of Treatment (CoTs) delivered which had DCP assistance

```{r DCP1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis(data = UDA_calendar_data,
                 dcp_data = DCP_data,
                 UDA_or_FP17 = "FP17",
                 level = "National",
                 region_STP_name = NULL)
```

-   This graph shows the percentage of CoTs carried out which benefited from involvement by Dental Care Practitioners.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.

## Percentage of total UDAs delivered which had DCP assistance by band

```{r DCP2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                             dcp_data = DCP_data,
                             UDA_or_FP17 = "UDA",
                             level = "National",
                             region_STP_name = NULL)
```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

# Patients seen

## Unique dental patients seen

```{r unique patients, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "National", 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

## Unique dental patients seen as a percentage of February 2020 figures

```{r unique patients percentage, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "National", 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

## Patients seen under the New Patient Premium definition
New Patient Premium metrics have been removed from this pack as the scheme has ended
<!-- ```{r npp activity, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_npp_activity(level = "National", 
                  region_STP_name = NULL, 
                  by_band = FALSE)
```

-   New Patient Premiums are part of the Dental Recovery Plan: <https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/>
-   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->

## Patients seen under the New Patient Premium definition by band
New Patient Premium metrics have been removed from this pack as the scheme has ended
<!-- ```{r npp activity by band, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_npp_activity(level = "National", 
                  region_STP_name = NULL, 
                  by_band = TRUE)
```

-   New Patient Premiums are part of the Dental Recovery Plan: <https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/>
-   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->

## Eligible contracts that have seen new patients

New Patient Premium metrics have been removed from this pack as the scheme has ended

<!-- COMMENTED OUT WHILE METHODOLOGY REVIEWED -->
<!-- ```{r npp contracts, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'} -->
<!-- plot <- plot_npp_contracts(level = "National", -->
<!--                            region_STP_name = NULL) -->

<!-- table <- table_npp_contracts(level = "National",  -->
<!--                              region_STP_name = NULL) -->

<!-- grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),  -->
<!--              layout_matrix = rbind(c(1, 1, 2))) -->
<!-- ``` -->

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: <https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/> -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->

## NPP activity to date against previous year's delivery

This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

<!-- COMMENTED OUT WHILE METHODOLOGY REVIEWED -->
<!-- ```{r npp comparison, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
<!-- plot <- plot_npp_activity_monitoring(level = "National", 
<!--                                      region_STP_name = NULL)

<!-- table <- table_npp_monitoring(level = "National", 
<!--                                      region_STP_name = NULL)

<!-- grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
<!--              layout_matrix = rbind(c(1, 1, 2)))
<!-- ```-->

<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources .-->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->

# Oral Health

## Oral health risk assessment

```{r BPE boxplot-revert, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_BPE_no_oral_health_risk(data = BPE_data,
                             level = "National",
                             region_STP_name = NULL)
```

-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.

# Units of Orthodontic Activity (UOA) Information

## Units of Orthodontic Activity - Calendar activity data standardised by working days

```{r UOA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "National",
                              region_STP_name = NULL)
```

-   These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs\*Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

## Units of Orthodontic Activity - Calendar year to date delivery

```{r YTD UOA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "National",
                          region_STP_name = NULL,
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

## Units of Orthodontic Activity started/completed

```{r YTD UOA completed started, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "National",
                          region_STP_name = NULL)
```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

# 111 Information

## 111 triage dental related call volumes

```{r 111 referrals, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_111_referrals()
```

-   This chart shows the demand for dental services via calls to 111.


# Appendix

## Description of terms used in this pack

-   **Calendar data** - This represents the month that a Course of Treatment (CoT) was completed.
-   **Scheduled data** - This represents the month that a Course of Treatment (CoT) was claimed for in the BSA Compass system.
-   **Course of Treatment (CoT)** - During a checkup, the dentist will identify any problems that need treatment. After discussing them with the patient, a Course of Treatment is created that deals with all of the problems.
-   **Unit of Dental Activity (UDA)** - Under the GDS contract, payments for primary care dentistry are made for units of dental activity (UDAs). <https://faq.nhsbsa.nhs.uk/knowledgebase/article/KA-01976>
-   **Treatment bands** - Treatment is grouped into bands which have UDAs associated with them. A brief overview is listed here
    -   **Band 1** - check up and simple treatment e.g. examination, x-rays and prevention advice (1 UDA)
    -   **Band 2** - mid range treatments e.g. fillings, extractions, and root canal work plus Band 1 work (3-7 UDAs)
    -   **Band 3** - includes complex treatments e.g. crowns, dentures, and bridges plus Band 1 and Band 2 work (12 UDAs)
    -   **Urgent** - a specified set of treatments delivered where oral health is likely to deteriorate significantly/ the person is in sever pain (1.2 UDAs)
    -   **Other** - mixed activity (0.75-1.2 UDAs)
-   **Contracted UDAs** - Agreed number of UDAs a provider will deliver in a financial year
-   **Delivered UDAs** - Actual number of UDAs a provider has delivered
-   **Foundation Dentists (FD)** - Foundation Dentists are newly qualified dentists who are undertaking additional training in a Dental Practice. They are excluded from metrics unless explicitly stated.
-   **FP17** - The form (electronic) Dental practices use to submit claims for finished courses of treatment to BSA via Compass. Data from these forms is used in these slides. <https://www.nhsbsa.nhs.uk/activity-payment-and-pension-services/dental-activity-processing>

Helpful reading <https://www.kingsfund.org.uk/insight-and-analysis/long-reads/dentistry-england-explained>


# Data sources

## Data sources

-   BSA calendar data received from BSA and added to NCDR
-   Tables are:
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_Contracts]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UDA_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UDA_Activity_FD_only]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_Unique_rolling]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_DCP]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_NPP_Eligible_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UOA_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental]/[Calendar_BPE]
-   R code used to create this pack is available on Github
    -   <https://github.com/nhsengland/SMT-Dental-Pack-PhODS>
-  Data used in this pack is published on FutureNHS along with national and regional packs
    -   <https://future.nhs.uk/DENTISTRY/view?objectID=39246768>
