---
title: "Dental Data Pack"
subtitle:  "National"
author: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  beamer_presentation:
    slide_level: 2
    toc: true
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
##always_allow_html: true
---


```{r libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(tidyverse)
library(downloadthis)
library(ggrepel)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')

#source in all file 
source(knitr::purl("SQLpulls.Rmd", output = tempfile()))
source(knitr::purl("Data_Processing.Rmd", output = tempfile()), local = TRUE)
source(knitr::purl("plotting.Rmd", output = tempfile()), local = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## UDA Activity Data

```{r UDA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "National", region_STP_name = NULL)`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).


* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.


## UDA activity- treatment data standardised by working days

```{r UDA_activity_Calendar2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "National",
                                             region_STP_name = NULL)
```

* The red trend line in the right graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.

* The black trend line shows the average performance of GDS contracts. In current financial year scaled up by 12.

## YTD UDA delivery

```{r YTD UDA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "National", 
                          region_STP_name = NULL, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```


## UOA activity- treatment data standardised by working days

```{r UOA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "National",
                                             region_STP_name = NULL)
```

* This data excludes contracts with zero or one annual contracted UOAs.

* The red trend line in the right graph shows an alternative method of calculating the denominator for contracted UOAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UOAs/12.

* The black trend line shows the average performance of contracts. In current financial year scaled up by 12.

## YTD UOA delivery
```{r YTD UOA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                          UDAorUOA = "UOA", 
                          level = "National", 
                          region_STP_name = NULL, 
                          all_regions_and_STPs = FALSE)
```


## 111 dental related call volumes

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_111_referrals()
```


