---
title: "Dental Data Pack"
subtitle: "`r params$region`"
date: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  xaringan::moon_reader:
    css: [theme.css, nhsr-fonts.css]
    self_contained: true
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
params:
  region: "North West"
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(ggrepel)
library(xaringanExtra)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')

#avoid standard form
options(scipen=999)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

#source(knitr::purl("SQLpulls.Rmd", output = tempfile()), local = TRUE)
#source(knitr::purl("Data_Processing.Rmd", output = tempfile()))
#source(knitr::purl("plotting.Rmd", output = tempfile()))
#source(knitr::purl("appendix_functions.Rmd", output = tempfile()))
```

```{r set ICB name, include=FALSE}

#get STPs for each region
if(params$region == "South West"){
  
  region <- "South West"
  
  STP1 <- "Bristol, North Somerset And South Gloucestershire ICB"
  STP2 <- "Dorset ICB"
  STP3 <- "Bath And North East Somerset, Swindon And Wiltshire ICB"
  STP4 <- "Somerset ICB"
  STP5 <- "Devon ICB"
  STP6 <- "Cornwall And The Isles Of Scilly ICB"
  STP7 <- "Gloucestershire ICB"
  STP8 <- NULL
  STP9 <- NULL
  STP10 <- NULL
  STP11 <- NULL
  
  STPs <- c(STP1, STP2, STP3, STP4, STP5, STP6, STP7)
  
  eval4 <- TRUE
  eval5 <- TRUE
  eval6 <- TRUE
  eval7 <- TRUE
  eval8 <- FALSE
  eval9 <- FALSE
  eval10 <- FALSE
  eval11 <- FALSE
  
}else if(params$region == "South East"){
  
  region <- "South East"
  
  STP1 <- "Sussex ICB"
  STP2 <- "Buckinghamshire, Oxfordshire And Berkshire West ICB"
  STP3 <- "Surrey Heartlands ICB"
  STP4 <- "Kent And Medway ICB"
  STP5 <- "Hampshire And Isle Of Wight ICB"
  STP6 <- "Frimley ICB"
  STP7 <- NULL
  STP8 <- NULL
  STP9 <- NULL
  STP10 <- NULL
  STP11 <- NULL
  
  STPs <- c(STP1, STP2, STP3, STP4, STP5, STP6)
  
  eval4 <- TRUE
  eval5 <- TRUE
  eval6 <- TRUE
  eval7 <- FALSE
  eval8 <- FALSE
  eval9 <- FALSE
  eval10 <- FALSE
  eval11 <- FALSE
  
}else if(params$region == "North West"){
  
  region <- "North West"
  
  STP1 <- "Greater Manchester ICB"
  STP2 <- "Cheshire And Merseyside ICB"
  STP3 <- "Lancashire And South Cumbria ICB"
  STP4 <- NULL
  STP5 <- NULL
  STP6 <- NULL
  STP7 <- NULL
  STP8 <- NULL
  STP9 <- NULL
  STP10 <- NULL
  STP11 <- NULL
  
  STPs <- c(STP1, STP2, STP3)
  
  eval4 <- FALSE
  eval5 <- FALSE
  eval6 <- FALSE
  eval7 <- FALSE
  eval8 <- FALSE
  eval9 <- FALSE
  eval10 <- FALSE
  eval11 <- FALSE
  
}else if(params$region == "North East And Yorkshire"){
  
  region <- "North East And Yorkshire"
  
  STP1 <- "Humber And North Yorkshire ICB"
  STP2 <- "South Yorkshire ICB"
  STP3 <- "North East And North Cumbria ICB"
  STP4 <- "West Yorkshire ICB"
  STP5 <- NULL
  STP6 <- NULL
  STP7 <- NULL
  STP8 <- NULL
  STP9 <- NULL
  STP10 <- NULL
  STP11 <- NULL
  
  STPs <- c(STP1, STP2, STP3, STP4)
  
  eval4 <- TRUE
  eval5 <- FALSE
  eval6 <- FALSE
  eval7 <- FALSE
  eval8 <- FALSE
  eval9 <- FALSE
  eval10 <- FALSE
  eval11 <- FALSE
  
}else if(params$region == "London"){
  
  region <- "London"
  
  STP1 <- "North Central London ICB"
  STP2 <- "South East London ICB"
  STP3 <- "North East London ICB"
  STP4 <- "South West London ICB"
  STP5 <- "North West London ICB"
  STP6 <- NULL
  STP7 <- NULL
  STP8 <- NULL
  STP9 <- NULL
  STP10 <- NULL
  STP11 <- NULL
  
  STPs <- c(STP1, STP2, STP3, STP4, STP5)
  
  eval4 <- TRUE
  eval5 <- TRUE
  eval6 <- FALSE
  eval7 <- FALSE
  eval8 <- FALSE
  eval9 <- FALSE
  eval10 <- FALSE
  eval11 <- FALSE
  
}else if(params$region == "Midlands"){
  
  region <- "Midlands"
  
  STP1 <- "Leicester, Leicestershire And Rutland ICB"
  STP2 <- "Herefordshire And Worcestershire ICB"
  STP3 <- "Nottingham And Nottinghamshire ICB"
  STP4 <- "Black Country ICB"
  STP5 <- "Staffordshire And Stoke-On-Trent ICB"
  STP6 <- "Northamptonshire ICB"
  STP7 <- "Shropshire, Telford And Wrekin ICB"
  STP8 <- "Lincolnshire ICB"
  STP9 <- "Birmingham And Solihull ICB"
  STP10 <- "Coventry And Warwickshire ICB"
  STP11 <- "Derby And Derbyshire ICB"
  
  STPs <- c(STP1, STP2, STP3, STP4, STP5, STP6, STP7, STP8, STP9, STP10, STP11)
  
  eval4 <- TRUE
  eval5 <- TRUE
  eval6 <- TRUE
  eval7 <- TRUE
  eval8 <- TRUE
  eval9 <- TRUE
  eval10 <- TRUE
  eval11 <- TRUE
  
}else if(params$region == "East Of England"){
  
  region <- "East Of England"
  
  STP1 <- "Hertfordshire And West Essex ICB"
  STP2 <- "Mid And South Essex ICB"
  STP3 <- "Norfolk And Waveney ICB"
  STP4 <- "Cambridgeshire And Peterborough ICB"
  STP5 <- "Bedfordshire, Luton And Milton Keynes ICB"
  STP6 <- "Suffolk And North East Essex ICB"
  STP7 <- NULL
  STP8 <- NULL
  STP9 <- NULL
  STP10 <- NULL
  STP11 <- NULL
  
  STPs <- c(STP1, STP2, STP3, STP4, STP5, STP6)
  
  eval4 <- TRUE
  eval5 <- TRUE
  eval6 <- TRUE
  eval7 <- FALSE
  eval8 <- FALSE
  eval9 <- FALSE
  eval10 <- FALSE
  eval11 <- FALSE
  
}

```

```{css, echo=F}
    /* Table width = 100% max-width */

    .remark-slide table{
        width: 100%;
    }

    /* Change the background color to white for shaded rows (even rows) */

    .remark-slide thead, .remark-slide tr:nth-child(2n) {
        background-color: white;
    }


```

#### Introduction

This slide pack has been streamlined to help users to easily access the most important information. This change took effect as of June 2024 data. As part of this change we have also sought to make the slides more useful by making the following changes:

-   Swapping from scheduled data (the month the dentist claimed for payment following a finished course of treatment) to calendar month data (the month the course of treatment finished). This change better reflects the activity of dentists.
-   Including only GDS/PDS/PDS+ contracts where total contracted UDAs \>100. This means contracts with low UDA targets are excluded because they are usually not monitored against UDA delivery.
-   The data is available in an Excel file available alongside this pack.

This pack will continue to evolve and change, any questions/comments should be directed to [england.primarycare.phodsdata@nhs.net](mailto:england.primarycare.phodsdata@nhs.net)

---

name: contents
#### Contents

- [Commissioned Units of Dental Activity (UDA) - Standardised by working days](#uda-conmmissioned)
- [Units of Dental Activity (UDA) - Calendar activity data standardised by working days](#uda-activity)
- [Units of Dental Activity (UDA) - Calendar year to date delivery](#ytd-uda-delivery)
- [Units of Dental Activity (UDA) - Monthly activity compared to previous financial year](#monthly-uda-activity)
- [Banded courses of treatment standardised by working days (including Foundation Dentists (FD))](#banded-CoT)
- [Banded Courses of treatment as % of February 2020 delivery (including FD)](#banded-CoT-Feb2020)
- [Percentage of total Courses of Treatment (CoTs) delivered which had DCP assistance](#DCP-CoT)
- [Percentage of total UDAs delivered which had DCP assistance by band](#DCP-UDA)
- [Unique dental patients seen](#unique-patients)
- [Unique dental patients seen as a percentage of February 2020 figures](#unique-patients-Feb2020)
- [Patients seen under the New Patient Premium definition](#NPP)
- [Patients seen under the New Patient Premium definition by band](#NPP-band)
- [Eligible contracts that have seen new patients](#NPP-contracts)
- [NPP activity to date against previous year's delivery](#NPP-comparison)
- [Oral health risk assessment](#BPE-contracts)
- [Units of Orthodontic Activity (UOA) - Calendar activity data standardised by working days](#UOA)
- [Units of Orthodontic Activity (UOA) - Calendar year to date delivery](#YTD-UOA-delivery)
- [Units of Orthodontic Activity (UOA) - Started/Completed](#YTD-UOA-STARTED)


---


name: uda-conmmissioned
#### Commissioned UDA - Standardised by working days

```{r xaringan-panelset-UDA_delivery_wd, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data, 
                                  level = "Regional",
                                  region_STP_name = region)


```


]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                             region_STP_name = STP1)

```


]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP2)
```


]
.panel[.panel-name[`r STP3`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP3)

```


]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval4}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP4)

```


]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval5}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP5)

```


]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval6}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP6)

```


]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval7}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP7)

```

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval8}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP8)

```


]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval9}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP9)

```


]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval10}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP10)

```


]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval11}
plot_historic_commissioned_UDA_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP11)

```


]

]

---

name: uda-activity
#### UDA - Calendar activity data standardised by working days

```{r xaringan-panelset-UDA_delivery_wd, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data, 
                                  level = "Regional",
                                  region_STP_name = region)


```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                             region_STP_name = STP1)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP2)
```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP3`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP3)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval4}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP4)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP5)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval6}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP6)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval7}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP7)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval8}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP8)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval9}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP9)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval10}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP10)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.


]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval = eval11}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "STP",
                                  region_STP_name = STP11)

```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

]

]

---

name: ytd-uda-delivery
#### UDA - Calendar year to date delivery

```{r xaringan-panelset-YTD_UDA_delivery, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "Regional", 
                          region_STP_name = region, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
 

```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP1, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)

```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP2, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP3, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP4, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP5, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP6, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP7, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP8, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP9, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP10, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "STP",
                          region_STP_name = STP11, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
]

---

name: monthly-uda-activity
#### UDA - Monthly activity compared to previous financial year

```{r xaringan-panelset-UDA_COM, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "Regional",
                                  region_STP_name = region)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP1)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.


]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP2)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP3)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP4)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP5)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP6)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP7)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP8)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP9)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP10)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data, 
                                  level = "STP", 
                                  region_STP_name = STP11)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows working days by month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

]
]


---

name: banded-CoT
#### Banded courses of treatment standardised by working days (including Foundation Dentists (FD))

```{r xaringan-panelset-banded_CoT, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data_FD, 
                level = "Regional", 
                region_STP_name = region, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data_FD, 
                level = "STP", 
                region_STP_name = STP1, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP2, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP3, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP4, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP5, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP6, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP7, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP8, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP9, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP10, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP11, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.
-   From November 2022 band 2 was split into 2a, 2b and 2c. More information can be viewed here: [Units of dental activity (UDA) changes to Band 2 treatments from Friday 25 November](https://www.nhsbsa.nhs.uk/units-dental-activity-uda-changes-band-2-treatments-friday-25-november)

]
]

---

name: banded-CoT-Feb2020
#### Banded Courses of Treatment as % of February 2020 delivery (including FD)

```{r xaringan-panelset-CoT_2020, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = region, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP1, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP2, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP3, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP4, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP5, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP6, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP7, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP8, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP9, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP10, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "STP", 
                region_STP_name = STP11, 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

]
]

---

name: DCP-CoT
#### Percentage of total Courses of Treatment (CoTs) delivered which had DCP assistance


```{r xaringan-panelset-DCP, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "Regional",
                  region_STP_name = region)
```
-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]

.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP1)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP2)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP3`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP3)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval4}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP4)

```
-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval5}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP5)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval6}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP6)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval7}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP7)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval8}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP8)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval9}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP9)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval10}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP10)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval11}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "STP",
                  region_STP_name = STP11)

```

-   This chart shows the percentage of FP17s carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
]
 ]



---

name: DCP-UDA
#### Percentage of total UDAs delivered which had DCP assistance by band

```{r xaringan-panelset-DCP2, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                              level = "Regional",
                              region_STP_name = region)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.
]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP1)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.
]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP2)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.
]
.panel[.panel-name[`r STP3`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP3)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.
]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval4}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP4)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP5)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval6}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP6)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval7}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP7)

```
-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.
]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval8}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP8)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval9}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP9)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval10}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP10)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5,eval=eval11}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                                             level = "STP",
                                             region_STP_name = STP11)

```

-   This chart shows the percentage of UDAs carried out which benefited from involvement by Dental Care Practitioners by treatment band.
-   DCP assistance data has been collected since October 2022 and DCP lead data collected since April 2024 so will likely take time for providers to improve reporting on it.
-   DCP lead data is only shown for Therapists as they deliver the majority of DCP-led activity.

]
 ]

---

name: unique-patients
### Unique dental patients seen

```{r xaringan-panelset-UDP, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]

-   Data on unique patients seen is not available at regional level, however ICB level data is available.


]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP1,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>


]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP2,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP3,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP4,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP5,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP6,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP7,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP8,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP9,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP10,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_unique_patients_rolling(level = "STP", 
                             region_STP_name = STP11,
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

]
]

---

name: unique-patients-Feb2020
### Unique dental patients seen as a percentage of February 2020 figures

```{r xaringan-panelset-UDP2, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]

-   Data on unique patients seen is not available at regional level, however ICB level data is available.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP1, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations


]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP2, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP3, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP4, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP5, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP6, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP7, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP8, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                              asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP9, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP10, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_unique_patients_rolling(level = "STP",
                                  region_STP_name = STP11, 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

]
]


---

name: NPP
#### Patients seen under the New Patient Premium definition

<!-- CODE COMMENTED OUT WHILE METHODOLOGY REVIEWED -->

```{r xaringan-panelset-NPP, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "Regional",
#                              region_STP_name = region,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP1,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP2,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP3,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP4,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP5,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP6,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP7,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP8,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP9,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP10,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP11,
#                  by_band = FALSE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
]


---

name: NPP-band
#### Patients seen under the New Patient Premium definition by band

```{r xaringan-panelset-NPP-band, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "Regional",
#                              region_STP_name = region,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP1,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP2,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP3,
 #                 by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP4,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP5,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended
]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP6,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP7,
 #                 by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP8,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP9,
 #                 by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP10,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
#plot_npp_activity(level = "STP",
#                                  region_STP_name = STP11,
#                  by_band = TRUE)

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
New Patient Premium metrics have been removed from this pack as the scheme has ended

]
]


---

name: NPP-contracts
#### Eligible contracts that have seen new patients


<!-- CODE COMMENTED OUT WHILE METHODOLOGY REVIEWED -->
```{r xaringan-panelset-NPP2, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_contracts(level = "Regional",
#                               region_STP_name = region)
# 
# table <- table_npp_contracts(level = "Regional",
#                               region_STP_name = region)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))


```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP1)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP1)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))


```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP2)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP2)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP3)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP3)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP4)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP4)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP5)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP5)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP6)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP6)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP7)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP7)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP8)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP8)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP9)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP9)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP10)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP10)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
# plot <- plot_npp_contracts(level = "STP",
#                                   region_STP_name = STP11)
# 
# table <- table_npp_contracts(level = "STP",
#                                   region_STP_name = STP11)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1),
#              layout_matrix = rbind(c(1, 1, 2)))

```

<!-- -   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/ -->
<!-- -   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
]

---


name: NPP-comparison
#### NPP activity to date against previous year's delivery
<!-- CODE COMMENTED OUT WHILE METHODOLOGY REVIEWED -->

```{r xaringan-panelset-NPP-comparison, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_activity_monitoring(level = "Regional", 
#                                      region_STP_name = region)
# 
# table <- table_npp_monitoring(level = "Regional", 
#                                      region_STP_name = region)
# 
# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.
]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}

# plot <- plot_npp_activity_monitoring(level = "STP", 
#                                      region_STP_name = STP1)
# 
# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP1)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))


```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_activity_monitoring(level = "STP", 
#                                     region_STP_name = STP2)

# table <- table_npp_monitoring(level = "STP", 
#                                     region_STP_name = STP2)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
# plot <- plot_npp_activity_monitoring(level = "STP", 
#                                      region_STP_name = STP3)

# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP3)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
# plot <- plot_npp_activity_monitoring(level = "STP", 
 #                                     region_STP_name = STP4)

# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP4)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))


```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
# plot <- plot_npp_activity_monitoring(level = "STP", 
#                                      region_STP_name = STP5)

# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP5)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))


```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
# plot <- plot_npp_activity_monitoring(level = "STP", 
#                                      region_STP_name = STP6)

# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP6)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
 #             layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
# plot <- plot_npp_activity_monitoring(level = "STP", 
#                                      region_STP_name = STP7)

# table <- table_npp_monitoring(level = "STP", 
 #                                     region_STP_name = STP7)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
# plot <- plot_npp_activity_monitoring(level = "STP", 
 #                                     region_STP_name = STP8)

# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP8)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
 #             layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
# plot <- plot_npp_activity_monitoring(level = "STP", 
 #                                     region_STP_name = STP9)

# table <- table_npp_monitoring(level = "STP", 
 #                                     region_STP_name = STP9)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
 #             layout_matrix = rbind(c(1, 1, 2)))


```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
# plot <- plot_npp_activity_monitoring(level = "STP", 
 #                                     region_STP_name = STP10)

# table <- table_npp_monitoring(level = "STP", 
 #                                     region_STP_name = STP10)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
#              layout_matrix = rbind(c(1, 1, 2)))


```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
# plot <- plot_npp_activity_monitoring(level = "STP", 
 #                                     region_STP_name = STP11)

# table <- table_npp_monitoring(level = "STP", 
#                                      region_STP_name = STP11)

# grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
 #             layout_matrix = rbind(c(1, 1, 2)))

```
<!-- -   Data before the NPP was introduced is taken from eDEN, while data after the introduction of the NPP (excluding unpaid) is from COMPASS. This is because it is not possible to replicate the COMPASS method on eDEN data to compare activity delivered prior to the NPP's introduction. The table shows the difference between COMPASS and eDEN data for months where we have both sources. -->
<!-- -   This data is not standardised by working day, so some of the difference between months may be due to differences in the number of working days. -->
This slide is not currently shown as the methodology is being reviewed. The data is available in the accompanying excel file.

]
]

---

name: BPE-contracts
#### Oral health risk assessment


```{r xaringan-panelset-BPE, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "Regional",
                              region_STP_name = region)

```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}

plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP1)


```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP2)

```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP3)

```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP4)


```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP5)


```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP6)

```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP7)


```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP8)

```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP9)


```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP10)


```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_BPE_no_oral_health_risk(data = BPE_data,
                              level = "STP",
                              region_STP_name = STP11)

```
-   This chart shows the percentage of contracts who assign recall intervals of less than a year to 50% or more of their low risk patients. 
-   Low risk patients are adult patients receiving routine care with no evidence of decay and a Basic Periodontal Examination (PBE) score of 0 or 1.
]
]

---

name: UOA
#### Units of Orthodontic Activity - Calendar activity data standardised by working days

```{r xaringan-panelset-UOA, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "Regional",
                              region_STP_name = region)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP1)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP2)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP3)
```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP4)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP5)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP6)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP7)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP8)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP9)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP10)

```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown.
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "STP",
                              region_STP_name = STP11)
```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. 
- Over the course of the financial year this graph allows us to see patterns of delivery.

]
]

---

name: YTD-UOA-delivery
#### Units of Orthodontic Activity - Calendar year to date delivery

```{r xaringan-panelset-UOA_YTD, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = region,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP1,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP2,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP3,
                          all_regions_and_STPs = FALSE)
```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP4,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP5,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP6,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP7,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP8,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP9,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP10,
                          all_regions_and_STPs = FALSE)

```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "STP",
                          region_STP_name = STP11,
                          all_regions_and_STPs = FALSE)
```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

]
]


---

name: YTD-UOA-STARTED
#### Units of Orthodontic Activity - Started/Completed

```{r xaringan-panelset-UOA_YTD_started, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[`r region`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "Regional",
                          region_STP_name = region)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP1`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP1)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP2`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP2)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP3`]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP3)
```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP4`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval4}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP4)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP5`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval5}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP5)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP6`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval6}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP6)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP7`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval7}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP7)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP8`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval8}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP8)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP9`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval9}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP9)

```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP10`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval10}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP10)
```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
.panel[.panel-name[`r STP11`]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center', eval=eval11}
plot_UOA_start_complete(data = UOA_calendar_data,
                          level = "STP",
                          region_STP_name = STP11)
```
- This graph shows the number of courses of orthodontic treatment started and completed in a month plus the UOAs delivered.
- FP17O forms are to be submitted at the start of orthodontic treatment and updated on completion. currently about 70% are updated with a completion date. 

]
]

---

### Data sources

-   BSA calendar data received from BSA and added to NCDR
-   Tables are:
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_Contracts]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UDA_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UDA_Activity_FD_only]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_Unique_rolling]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_DCP]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_NPP_Eligible_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UOA_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental]/[Calendar_BPE]
-   R code used to create this pack is available on Github
    -   <https://github.com/nhsengland/SMT-Dental-Pack-PhODS>
-  Data used in this pack is published on FutureNHS along with national and regional packs
    -   <https://future.nhs.uk/DENTISTRY/view?objectID=39246768>
