---
title: "Dental Data Pack"
subtitle: "National"
date: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  xaringan::moon_reader:
    css: [theme.css, nhsr-fonts.css]
    self_contained: true
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(ggrepel)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')

#avoid standard form
options(scipen=999)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, message =FALSE, include=FALSE}
source(knitr::purl("SQLpulls.Rmd", output = tempfile()), local = TRUE)
```

```{r, message =FALSE, include=FALSE}
source(knitr::purl("Data_Processing.Rmd", output = tempfile()))
```

```{r, message =FALSE, include=FALSE}
source(knitr::purl("plotting.Rmd", output = tempfile()))
```


name: contracts-table

```{css, echo=F}
    /* Table width = 100% max-width */

    .remark-slide table{
        width: 100%;
    }

    /* Change the background color to white for shaded rows (even rows) */

    .remark-slide thead, .remark-slide tr:nth-child(2n) {
        background-color: white;
    }
```


<!---

### UDA Activity Data

```{r xaringan-panelset-UDA_delivery_wd, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r UDA_delivery_wd1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "National", region_STP_name = NULL)`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.



]
.panel[.panel-name[South East]
```{r UDA_delivery_wd2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "South East")
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "South East")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.


]
.panel[.panel-name[South West]
```{r UDA_delivery_wd3, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "South West")
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "South West")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.


]
.panel[.panel-name[North West]
```{r UDA_delivery_wd4, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "North West")
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "North West")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.


]
.panel[.panel-name[North East and Yorkshire]
```{r UDA_delivery_wd5, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "North East And Yorkshire")

```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "North East and Yorkshire")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.


]
.panel[.panel-name[London]
```{r UDA_delivery_wd6, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "London")

```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "London")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.

]
.panel[.panel-name[Midlands]
```{r UDA_delivery_wd7, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "Midlands")

```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "Midlands")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.


]
.panel[.panel-name[East of England]
```{r UDA_delivery_wd8, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_wd(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "East Of England")
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "East of England")`** GDS contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).

* The blue line in the graph shows an alternative method of calculating the denominator for contracted UDAs expected each month. Here the denominator is annual contracted UDAs * monthly working days/annual working days. The usual denominator is annual contracted UDAs/12.
]
.panel[.panel-name[All]
```{r UDA_delivery_wd9, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_all_regions(data = UDA_calendar_data, 
                                              UDAorUOA = "UDA",
                                              level = "National",
                                              region_STP_name = NULL,
                                              plotChart = TRUE, 
                                              all_regions_and_STPs = TRUE)
```

]

]

-->


### UDA activity- treatment data standardised by working days

```{r xaringan-panelset-historic_UDA_delivery_wd, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r historic_UDA_delivery_wd1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "National",
                                            region_STP_name = NULL)

```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 
]

 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "South East")

```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 

 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "South West")

```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 

 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "North West")
```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 

 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data, 
                                             level = "Regional",
                                             region_STP_name = "North East And Yorkshire")
```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 
 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data, 
                                             level = "Regional",
                                             region_STP_name = "London")
```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 
 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data, 
                                             level = "Regional",
                                             region_STP_name = "Midlands")
```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 
 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data, 
                                             level = "Regional",
                                             region_STP_name = "East Of England")
```
* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days). 
]
.panel[.panel-name[All]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_all_regions(data = UDA_calendar_data, 
                                              UDAorUOA = "UDA",
                                              level = "National",
                                              region_STP_name = NULL,
                                              plotChart = TRUE, 
                                              all_regions_and_STPs = TRUE)
```
* This data excludes contracts with zero or one annual contracted UDAs.

* The denominator is annual contracted UDAs * (monthly working days/annual working days). 
 ]
 ]

---
### YTD UDA delivery

```{r xaringan-panelset-YTD_UDA_UOA_delivery, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "National", 
                          region_STP_name = NULL, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}

plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "South East")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "South West")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[North West]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "North West")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "North East And Yorkshire")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "London")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "Midlands")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                                  UDAorUOA = "UDA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "East Of England")
```
* This data excludes contracts with zero or one annual contracted UDAs.

]

]

---
### UOA activity- treatment data standardised by working days

```{r xaringan-panelset-historic_UOA_delivery_wd, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "National",
                                             region_STP_name = NULL)

```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "South East")


```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "South West")

```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[North West]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "North West")

```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "North East And Yorkshire")

```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "London")

```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "Midlands")


```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "Regional",
                                             region_STP_name = "East Of England")

```
* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

]
.panel[.panel-name[All]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_all_regions(data = UOA_calendar_data, 
                                              UDAorUOA = "UOA",
                                              level = "National",
                                              region_STP_name = NULL,
                                              plotChart = TRUE, 
                                              all_regions_and_STPs = TRUE)
```
* This data excludes contracts with zero or one annual contracted UDAs.

* The denominator is annual contracted UDAs * (monthly working days/annual working days). 
]
]
---

### YTD UOA delivery

```{r xaringan-panelset-YTD_UOA_delivery, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                          UDAorUOA = "UOA", 
                          level = "National", 
                          region_STP_name = NULL, 
                          all_regions_and_STPs = FALSE)

```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}

plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "South East")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "South West")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[North West]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "North West")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "North East And Yorkshire")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "London")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "Midlands")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                                  UDAorUOA = "UOA",
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  level = "Regional",
                                  region_STP_name = "East Of England")
```
* This data excludes contracts with zero or one annual contracted UOAs.

]

]

---

### Time series of banded Courses of Treatment

```{r xaringan-panelset-YTD_UOA_delivery, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "National", 
                region_STP_name = NULL, 
                plotChart = TRUE
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "South East", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "South West", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[North West]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "North West", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "North East and Yorkshire", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "London", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "Midlands", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "East of England", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = FALSE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]

]

---

### Banded Courses of Treatment as % of 2019 delivery

```{r xaringan-panelset-YTD_UOA_delivery, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "South East", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "South West", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[North West]
```{r  echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "North West", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "North East and Yorkshire", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "London", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "Midlands", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "Regional", 
                region_STP_name = "East of England", 
                plotChart = TRUE,
                all_regions_and_STPs = FALSE,
                asIndex = TRUE)
```
* This data excludes contracts with zero or one annual contracted UOAs.

]

]

---

name: 111-call-volumes

### 111 dental related call volumes

```{r xaringan-panelset-111_volumes_breakdown, echo=FALSE}
xaringanExtra::use_panelset()
```

 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_111_referrals()
```


 ]
  .panel[.panel-name[National breakdown by disposition]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_breakdown_111_referrals()
```


 ]
 ]



