---
title: "Dental Data Pack"
subtitle:  "National"
author: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  beamer_presentation:
    latex_engine: pdflatex
    slide_level: 2
    toc: true
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
##always_allow_html: true
---

```{r libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(ggrepel)
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(dplyr)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')

#source in all files
source(knitr::purl("SQLpulls.Rmd", output = tempfile()), local = TRUE)
source(knitr::purl("Data_Processing.Rmd", output = tempfile()))
source(knitr::purl("plotting.Rmd", output = tempfile()))
source(knitr::purl("appendix_functions.Rmd", output = tempfile()))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

## Introduction

This slide pack has been streamlined to help users to easily access the most important information. This change took effect as of June 2024 data. As part of this change we have also sought to make the slides more useful by making the following changes:

-   Swapping from scheduled data (the month the dentist claimed for payment following a finished course of treatment) to calendar month data (the month the course of treatment finished). This change better reflects the activity of dentists.
-   Including only GDS/PDS/PDS+ contracts where total contracted UDAs \>100. This means contracts with low UDA targets are excluded because they are usually not monitored against UDA delivery.
-   A national HTML will no longer be produced, instead the data is in an Excel file available alongside this pack.

#### Metrics and outputs soon to be added

-   Oral health risk assessments

&nbsp; <!--This is to force a line break-->

ICB level data is now included in the HTML files.

&nbsp; <!--This is to force a line break-->

This pack will continue to evolve and change, any questions/comments should be directed to [england.primarycare.phodsdata@nhs.net](mailto:england.primarycare.phodsdata@nhs.net)

## Calendar vs scheduled data

Analyses in this report now only use **calendar data**. Previous packs used scheduled data. An explanation on the difference is given below. The appendix also provides more detail on how the switch effects the data.

#### Calendar data explanation

-   Calendar data represents the month that a Course of Treatment (CoT) was completed.
-   For calendar data, if a CoT was completed in February but not declared till March, that activity would still be recorded as occurring in February.

#### Scheduled data explanation

-   Scheduled data represents the month that a Course of Treatment (CoT) was claimed for in the BSA Compass system.
-   For scheduled data, if a CoT was completed in February but not declared till March, the financial activity would recorded as occurring in March.

&nbsp; <!--This is to force a line break-->

The swap to using calendar data allows us to more accurately see what activity is happening per month rather than what payments are being claimed per month.

&nbsp; <!--This is to force a line break-->

Note that following a finished Course of Treatment (CoT), dentists have 62 days to declare their activity via FP17 forms to the BSA Compass system. This means when using calendar data, the most recent two months data are incomplete and subject to change, particularly for the most recent month. We expect final data to be higher.

# Units of Dental Activity (UDA) Information

## Units of Dental Activity - Calendar activity data standardised by working days

```{r UDA_activity_Calendar2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                              level = "National",
                              region_STP_name = NULL)
```

-   These graphs show the percentage of UDAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UDAs\* Monthly working days/working days per year.
-   For the current financial year, monthly performance is shown. For the previous financial years, annual average performance is shown.
-   Over the course of the financial year this graph allows us to see patterns of delivery.

## Units of Dental Activity - Calendar year to date delivery

```{r YTD UDA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "National",
                          region_STP_name = NULL,
                          plotChart = TRUE,
                          all_regions_and_STPs = FALSE)
```

-   This graph shows the progress towards delivering against contracted UDAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

## Units of Dental Activity - Monthly activity compared to previous financial year

```{r monthly UDAs, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height = 5, fig.align = 'center'}
plot <- plot_monthly_uda_delivered(data = UDA_calendar_data,
                                   level = "National", 
                                   region_STP_name = NULL)

table <- table_working_days()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

- This graph shows the number of UDAs delivered each month for the current financial year compared with the previous financial year.
- Some of the difference between months may be due to differences in the number of working days. The table shows the number of working days in each month for 2023/24 and 2024/25.
- As dentists have 62 days to claim for their activity, the most recent two months data are incomplete. We expect final data to be higher. Figures for the latest complete month of data are presented on this graph.

## Banded courses of treatment standardised by working days (including Foundation Dentists (FD))

```{r banded CoT 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align="center"}
plot_banded_CoT(data = UDA_calendar_data_FD, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = FALSE)
```

-   This graph shows the number of completed Courses of Treatment (CoTs) by band over time. Data has been standardised to working days to remove variation due to month length. It is calculated as completed CoTs\*Monthly working days/working days per year.

## Banded Courses of Treatment as % of February 2020 delivery (including FD)

```{r banded CoT 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_banded_CoT(data = UDA_calendar_data_FD, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = TRUE)
```

-   This graph shows time series on the the number of completed Courses of Treatment (CoTs) by band compared to pre-Covid delivery.

# Dental Care Practitioners (DCPs) Information

## Percentage of total Courses of Treatment (CoTs) delivered which had DCP assistance

```{r DCP1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis(data = UDA_calendar_data,
                  dcp_data = DCP_data,
                  UDA_or_FP17 = "FP17",
                  level = "National",
                  region_STP_name = NULL)
```

-   This graph shows the percentage of UDAs carried out which benefited from assistance by Dental Care Practitioners. DCP data has been collected since October 2022 so will likely take time for providers to improve reporting on it.

## Percentage of total UDAs delivered which had DCP assistance by band

```{r DCP2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_DCP_analysis_band(data = UDA_calendar_data,
                              dcp_data = DCP_data,
                              UDA_or_FP17 = "UDA",
                              level = "National",
                              region_STP_name = NULL)
```

-   This chart shows the percentage of UDAs carried out which benefited from assistance by Dental Care Practitioners by treatment band. DCP data has been collected since October 2022 so will likely take time for providers to improve reporting on it.

# Patients seen

## Unique dental patients seen

```{r unique patients, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "National", 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = FALSE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months. <https://www.nice.org.uk/guidance/cg19/chapter/Recommendations>

## Unique dental patients seen as a percentage of February 2020 figures

```{r unique patients percentage, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_unique_patients_rolling(level = "National", 
                             plotChart = TRUE, 
                             all_regions_and_STPs = FALSE, 
                             asIndex = TRUE)
```

-   This chart shows the number of unique patients seen in a 24 month period for adults, and 12 month period for children compared to February 2020 levels.
-   A person seen more than once in the rolling 12/24 months would be counted only once.
-   NICE guidelines recommend that children should be seen at least 12 months and adults at least every 24 months.https://www.nice.org.uk/guidance/cg19/chapter/Recommendations

## Patients seen under the New Patient Premium definition

```{r npp activity, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_npp_activity(level = "National", 
                  region_STP_name = NULL)
```

-   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/
-   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment.

## Eligible contracts that have seen new patients

```{r npp contracts, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot <- plot_npp_contracts(level = "National",
                           region_STP_name = NULL)

table <- table_npp_contracts(level = "National", 
                             region_STP_name = NULL)

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

-   New Patient Premiums are part of the Dental Recovery Plan: https://www.england.nhs.uk/long-read/update-on-the-dental-recovery-plan/
-   The New Patient Premium scheme started in March 2024. Dentists are paid on completion of a course of treatment.

# Units of Orthodontic Activity (UOA) Information

## Units of Orthodontic Activity - Calendar activity data standardised by working days

```{r UOA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                              level = "National",
                              region_STP_name = NULL)
```

- These graphs show the percentage of UOAs delivered compared to the expected delivery. Expected monthly delivery is standardised by working days in the month and calculated as Target UOAs*Monthly working days/working days per year.
- For the current financial year, monthly performance is shown. Historic data is not yet available for this chart.
- Over the course of the financial year this graph allows us to see patterns of delivery.

## Units of Orthodontic Activity - Calendar year to date delivery

```{r YTD UOA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "National",
                          region_STP_name = NULL,
                          all_regions_and_STPs = FALSE)
```

- This graph shows the progress towards delivering against contracted UOAs in the financial year. Here, expected delivery assumes delivery is equal across all months.

# 111 Information

## 111 triage dental related call volumes

```{r 111 referrals, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_111_referrals()
```

-   This chart shows the demand for dental services via calls to 111.

<!-- # BPE Information -->
<!-- ## Oral health risk assessment -->

```{r BPE boxplot-revert, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
# 
# plot_BPE_no_oral_health_risk(data = BPE_data,
#                              level = "National",
#                              region_STP_name = NULL)

```


# Appendix

## Description of terms used in this pack

-   **Calendar data** - This represents the month that a Course of Treatment (CoT) was completed.
-   **Scheduled data** - This represents the month that a Course of Treatment (CoT) was claimed for in the BSA Compass system.
-   **Course of Treatment (CoT)** - During a checkup, the dentist will identify any problems that need treatment. After discussing them with the patient, a Course of Treatment is created that deals with all of the problems.
-   **Unit of Dental Activity (UDA)** - Under the GDS contract, payments for primary care dentistry are made for units of dental activity (UDAs). <https://faq.nhsbsa.nhs.uk/knowledgebase/article/KA-01976>
-   **Treatment bands** - Treatment is grouped into bands which have UDAs associated with them. A brief overview is listed here
    -   **Band 1** - check up and simple treatment e.g. examination, x-rays and prevention advice (1 UDA)
    -   **Band 2** - mid range treatments e.g. fillings, extractions, and root canal work plus Band 1 work (3-7 UDAs)
    -   **Band 3** - includes complex treatments e.g. crowns, dentures, and bridges plus Band 1 and Band 2 work (12 UDAs)
    -   **Urgent** - a specified set of treatments delivered where oral health is likely to deteriorate significantly/ the person is in sever pain (1.2 UDAs)
    -   **Other** - mixed activity (0.75-1.2 UDAs)
-   **Contracted UDAs** - Agreed number of UDAs a provider will deliver in a financial year
-   **Delivered UDAs** - Actual number of UDAs a provider has delivered
-   **Foundation Dentists (FD)** - Foundation Dentists are newly qualified dentists who are undertaking additional training in a Dental Practice. They are excluded from metrics unless explicitly stated.
-   **FP17** - The form (electronic) Dental practices use to submit claims for finished courses of treatment to BSA via Compass. Data from these forms is used in these slides. <https://www.nhsbsa.nhs.uk/activity-payment-and-pension-services/dental-activity-processing>

Helpful reading <https://www.kingsfund.org.uk/insight-and-analysis/long-reads/dentistry-england-explained>

## Impact of swapping to calendar data for dentistry

-   Dental activity data can be grouped into months using two different methods - by 'calendar' month or by 'scheduled' month.

-   Using calendar month means that activity is allocated to months based on the month in which the course of treatment finished.

-   Using scheduled month means that activity is allocated to months based on the month the dentist claimed for payment following a finished course of treatment.

-   This pack has switched from using scheduled data to calendar data to better reflect when dental activity occurs.

-   Dentists have 62 days following the completion of a course of treatment to claim payment. This means that the latest two months of any charts using activity data should now be considered provisional, as more claims for treatment ending in these months can be submitted.

-   While the last two months of activity data will be incomplete, UDA claim patterns indicate that most activity is claimed for in the same month as treatment finished.

-   For example, for treatment ending in December 2023:

    -   90% was submitted in December 2023.

    -   9% was submitted in January 2024.

    -   1% was submitted in February 2024.

## Comparison of monthly UDA data

Switching to calendar data means that spikes in the number of claims submitted due to submission arrangements are smoothed out.

```{r time series comparison, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14}
plot <- plot_time_series_comparison()
table <- table_time_series_comparison()

grid.arrange(plot, table, nrow = 1, widths = c(1, 1, 1), 
             layout_matrix = rbind(c(1, 1, 2)))
```

# Data sources

## Data sources

-   BSA calendar data received from BSA and added to NCDR
-   Tables are:
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_Contracts]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UDA_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UDA_Activity_FD_only]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_Unique_rolling]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_DCP]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_NPP_Eligible_Activity]
    -   [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[Calendar_UOA_Activity]
-   R code used to create this pack is available on Github
    -   <https://github.com/nhsengland/SMT-Dental-Pack-PhODS>
