---
title: "Dental Data Pack"
subtitle:  "National"
author: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  beamer_presentation:
    slide_level: 2
    toc: true
    includes:
      in_header: slide_format2.tex
  slidy_presentation: default
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
##always_allow_html: true
---


```{r libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable)
library(downloadthis)
library(lubridate)
library(knitr)
library(ggrepel)
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
options(knitr.duplicate.label = 'allow')

#source in all file 
source(knitr::purl("SQLpulls.Rmd", output = tempfile()))
source(knitr::purl("Data_Processing.Rmd", output = tempfile()), local = TRUE)
source(knitr::purl("plotting.Rmd", output = tempfile()), local = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# UDA Infomation
## UDA activity- treatment data standardised by working days

```{r UDA_activity_Calendar2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UDA_delivery_wd(data = UDA_calendar_data,
                                             level = "National",
                                             region_STP_name = NULL)
```

* This data excludes contracts with zero or one annual contracted UDAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UDAs * (monthly working days/annual working days).

## YTD UDA delivery

```{r YTD UDA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UDA_calendar_data, 
                          UDAorUOA = "UDA", 
                          level = "National", 
                          region_STP_name = NULL, 
                          plotChart = TRUE, 
                          all_regions_and_STPs = FALSE)
```
* This data excludes contracts with zero or one annual contracted UDAs.

# UOA Information
## UOA activity- treatment data standardised by working days

```{r UOA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_historic_UOA_delivery_wd(data = UOA_calendar_data,
                                             level = "National",
                                             region_STP_name = NULL)
```

* This data excludes contracts with zero or one annual contracted UOAs.

* For the previous financial year, the black trend line shows the average performance. In current financial year the denominator is annual contracted UOAs * (monthly working days/annual working days). 

## YTD UOA delivery
```{r YTD UOA, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_YTD_UDA_UOA_delivery(data = UOA_calendar_data, 
                          UDAorUOA = "UOA", 
                          level = "National", 
                          region_STP_name = NULL, 
                          all_regions_and_STPs = FALSE)
```
* This data excludes contracts with zero or one annual contracted UDAs.

## Time series of banded Courses of Treatment
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align="center"}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = FALSE)
```

## Banded Courses of Treatment as % of 2019 delivery
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align="center}
plot_banded_CoT(data = UDA_calendar_data, 
                level = "National", 
                region_STP_name = NULL, 
                asIndex = TRUE)
```

# 111 Information

## 111 dental related call volumes

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_111_referrals()
```


